% Copyright 2024 Nekostein, an unincorporated game development team consisting of Neruthes and MIAO_OAIM.
% Published with CC BY-NC 4.0 license.
% Permission is granted that you may use this LaTeX template to generate documents for your own unincorporated organization.


% This is a series of documents that the President may sign
% to express their intention of representing the unincorporated organization.


\documentclass[12pt,a4paper,hidelinks]{article}
\usepackage[textwidth=35em,vmargin=20mm]{geometry}
\usepackage{calc,fontspec,xcolor,graphicx,microtype,paralist,enumitem,tabu,booktabs,datetime2,xeCJK,hyperref}

\usepackage{termes-otf}
% \usepackage{nimbussans}
% \usepackage{XCharter}
% \usepackage{lmodern}
% \setromanfont{Lora}
% \setmainfont{Lora}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\linespread{1}
\frenchspacing

\input{.workdir/fulltomldata.texpart}
\input{.workdir/tomldata2tex.texpart}


\newcommand{\hsepline}[0]{
    \nopagebreak\par\nopagebreak\vskip 0.5em%
    \begin{center}%
        \rmfamily\normalsize\mdseries%
        *~~~~~~*~~~~~~*%
    \end{center}
}
\newcommand{\newdochere}[1]{
    \setcounter{page}{1}
    \setcounter{section}{0}
    \scalebox{1}[1.13]{%
        \parbox{\textwidth}{%
            \begin{center}%
                % \large
                \rmfamily\mdseries\strut%
                #1%
            \end{center}%
        }%
    }%
    \par
}
\newcommand{\stdorginfo}[0]{
    \parbox{\linewidth}{
        \tabcolsep=0pt
        \small
        \begin{tabu}{lX}
            \toprule
            \mdseries Business Name~~~~~~ & \fulltomldataATfullname \\
            \mdseries Date of Creation & \fulltomldataATdatecreation \\
            \mdseries Business Type & \fulltomldataATtype \\
            \mdseries President & \fulltomldataATpresident \\
            \mdseries Charter & \uninctomldataATwitnessFIRST \\
            \mdseries Charter Hash & \fulltomldataATcharterhash \\
            \bottomrule
        \end{tabu}
    }\par\vskip 14pt
}
\newcommand{\stdsignaturearea}[1]{
    #1\par
    \parbox{\linewidth}{
        \tabcolsep=0pt
        \small
        \begin{tabu}{XXX}
            \strut Signature/Stamp/Seal & & \strut Date\\
            \hline
        \end{tabu}
    }
}





\begin{document}
\newdochere{INTRODUCTION\\HOW TO USE THIS DOCUMENT}
\thispagestyle{empty}

Now you are seeing the PMisc document, a PDF built via \LaTeX.
It is generated from ``UNINC.toml'' and ``pmisc.tex'' in the UNINCDB repository.

In this document, we offer a few pre-made forms
that an unincorporated organization can print and sign/stamp/seal en masse.
For example, the Deed Poll for Assuming Presidential Duty can be instrumental
in convincing a third party that any organizational liability that may possibly emerge
will at least be handled by the President in person.

You might have noticed that using this tool does not necessarily require obtaining a Letter of Witness
for your Charter from Nekostein or any other witness authority.
All you need is to make a local git clone and fill up data in the ``/db-private/1970/myorg'' directory.
The usage is straightforward and the scripts are easy to understand.

But for technical robustness, requesting a Letter of Witness will be a good idea to keep your local data consistent.
If the Charter is witnessed by the Nekostein-hosted UNINCDB,
this PDF should be available at the following URL.

\begin{center}
    \href{\unincdbaltdocprefix.pmisc.pdf}{\unincdbaltdocprefix.pmisc.pdf}
\end{center}

\hsepline

\vfill
\begingroup\small
Copyright \copyright~2024 Nekostein, an unincorporated game development team consisting of Neruthes and MIAO\_OAIM.
Published with CC BY-NC 4.0 license.
Permission is granted that you may use this \LaTeX{} template to generate documents for your own unincorporated organization.

This PDF is generated on \today.
\endgroup





\clearpage
\newdochere{DEED POLL\\FOR ASSUMING PRESIDENTIAL DUTY}
\thispagestyle{empty}

\stdorginfo

\strut I,
\underline{\fulltomldataATpresident},
as the President of unincorporated organization

\underline{\fulltomldataATfullname}

hereby make a solemn declaration of FOUR clauses:

\begin{enumerate}
    \item I shall exercise Presidential rights in the unincorporated organization owing fiduciary duty to the Charter
        identifiable with the given 160-bit SHA-1 hash:\\
        \underline{\fulltomldataATcharterhash}.
    \item In the event that an organizational resolution, requiring the inauguration of a new President,
        is approved in accordance with the Charter, I shall transfer all Presidential rights,
        as well as any applicable documentation, to the new President.
    \item Any asset that I control on behalf of the organization shall be passed to the new President
        in the event of my resigning, retirement, or death.
    \item In the event that our Charter is being amended, or significant manifest information
        (e.g. President, Secretary, Addresses) is being changed,
        I shall publish an announcement online, and shall notify the following witness authorities,
        as long as they remain operational and free of charge,
        to ensure best possible availability of information.
        \begin{compactitem}
            \uninctomldataATwitnessITEM
        \end{compactitem}
\end{enumerate}

This is a computer-generated document that shall come into force
if and only if its printed copy is signed off.

\hsepline

\vfill
\stdsignaturearea{}








\clearpage
\newdochere{\fulltomldataATfullname\\\MakeUppercase{Statement on Adopting Official Stamps/Seals}}
\thispagestyle{empty}

\stdorginfo

This is to certify that the following (quantity: \underline{\hspace{10em}})
stamps/seals belong to this unincorporated organization.
These stamps may be used to indicate approval in civil and commerce terms on behalf of our organization.
All previous similar declarations are invalid since today.

We may publish a scanned copy of this document at the following web address.
If we do, this printed statement must conform to the online copy to remain valid;
it is a formal way of delivering invalidation announcements.

\providecommand{\fulltomldataATcomDOTnekosteinDOTurlstamps}[0]{}
\strut URL:~~\fulltomldataATcomDOTnekosteinDOTurlstamps

\begin{tabu}{|X|X|X|}
    \hline
    Stamp Sample 1 & Stamp Sample 2 & Stamp Sample 3\\ & &\vspace{30mm} \\
    \hline
    Stamp Sample 4 & Stamp Sample 5 & Stamp Sample 6\\ & &\vspace{30mm} \\
    \hline
    Stamp Sample 7 & Stamp Sample 8 & Stamp Sample 9\\ & &\vspace{30mm} \\
    \hline
\end{tabu}

% \vfill
\stdsignaturearea{By President:}\par
Witness / Endorsement / Notary:
\vfill






\clearpage
\newdochere{\fulltomldataATfullname\\\MakeUppercase{Certificate of Power of Attorney}}
\thispagestyle{empty}

\stdorginfo

\strut This is to certify that the person

\vskip 1em
\underline{\strut\hspace{0.8\linewidth}}
\vskip 1em

has the power of attorney to sign off paperwork,
on behalf of our organization,
within the following categories:

\vskip 1em
\underline{\strut\hspace{0.8\linewidth}}
\vskip 1em

Valid through
\vskip 1em

(date: \underline{\hspace{15em}}).

\hsepline

\vfill
\stdsignaturearea{By President:}
\end{document}
