% Copyright (c) 2024-2025 Nekostein (https://nekostein.com/). All rights reserved.
% Redistribution is permitted as part of the "unincdb" repository. Do not use otherwise.


\input{_dist/libvi/latex/ns-letter.tex}
\usepackage{hyphenat,fontspec}
% \newgeometry{textwidth=33em,rmargin=25mm,tmargin=90mm,bmargin=37mm}
\geometry{textwidth=33em,rmargin=25mm,tmargin=55mm,bmargin=37mm}
\sloppy


\setlength{\sendtoareaextraraise}{58.5pt}
% \emergencystretch=15em % Allow extra stretching in case of overfull lines






% ----------------------------------------------------------
% BEGIN Pandoc compatibility layer
\providecommand{\tightlist}[0]{%
    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
}
\providecommand{\url}[1]{#1}
% \providecommand{\arraybackslash}[0]{}
% END Pandoc compatibility layer
% ----------------------------------------------------------






\newcommand{\hsepline}[0]{
    \nopagebreak\par\nopagebreak\vskip 0.5em%
    \begin{center}%
        \rmfamily\normalsize\mdseries%
        *~~~~~~*~~~~~~*%
    \end{center}
}


\newcommand{\fakenewdoc}[0]{
    \setcounter{section}{0}
}

\newcounter{minititleding}
\setcounter{minititleding}{171}
\newcommand{\minititle}[1]{
    \toparea{%
        \center%
        \Large\bfseries\sffamily%
        #1%
        \par\hsepline%
    }\leavevmode\vskip 30mm
}
\newcommand{\cachedunincname}[0]{}
\newcommand{\manifestfieldbig}[2]{
    {\small\strut#1}\par%
    \textbf{\sffamily\normalsize{\strut#2}}%
    \vskip 1em
}
\newcommand{\manifestfield}[2]{
    \parbox[t]{9.5em}{\small\strut#1}\hfill%
    \parbox[t]{\linewidth-10em}{\small\raggedright\mdseries{\strut#2}}\par
}


\makeatletter
\renewcommand{\verbatim@font}[0]{\ttfamily\footnotesize}
\makeatother

\input{.workdir/UNINC.toml.Nekostein.regno.texpart}



\begin{document}
\setupdecorations
\minititle{\strut LETTER OF WITNESS FOR\\\strut UNINCORPORATED ORGANIZATION}


This is to certify that the following unincorporated organization has been filed
with a Charter identifiable with the given hash.
\vskip 1em

\input{.workdir/UNINC.toml.Nekostein.1.texpart}


\vfill

\small
\strut Date: \today\\
\strut\unincregnohref



\clearpage
\rmfamily\normalsize








% Organization Charter
\fakenewdoc
\minititle{\strut ATTACHMENT 1\\\strut ORGANIZATION CHARTER}\small
\addfontfeatures{Ligatures=TeX}

\input{.workdir/Charter.md.texpart}\hsepline
\clearpage





% And then the Appendix
\fakenewdoc
\minititle{\strut ATTACHMENT 2\\\strut FILING APPENDIX}

This piece of text, known as ``Filing Appendix'', is afforded by the unincorporated organization
and therefore shall not be interpreted as written by or endorsed by the witness authority.

\hsepline

\input{.workdir/Appendix.md.texpart}\hsepline
\clearpage





% Extra Statement
\fakenewdoc
\minititle{\strut ATTACHMENT 3\\\strut STATUTORY STATEMENT BY NEKOSTEIN}
\footnotesize


\section{Intellectual Properties}
\begin{enumerate}
    \tightlist
    \item The letter template of this document is a copyrighted work of typography.
    \item The ``Nekostein'' wordmark and the ``excited cat face'' picture may be unregistered trademarks of Nekostein.
    \item Permission of redistribution is granted to the extent of sharing this digital PDF,
        and subsequently its printed copies and screenshots.
    \item Nekostein is an unincorporated game development team consisting of Neruthes and MIAO\_OAIM.
    \item For more information, visit our website at ``\href{https://nekostein.com/}{https://nekostein.com/}''.
\end{enumerate}

\section{Miscellaneous}
\begin{enumerate}
    \tightlist
    \item The organization mentioned in this document might not necessarily update this UNINCDB record
        every time its metadata or Charter is amended.
        UNINCDB does not necessarily guarantee information being up-to-date.
    \item The index of our UNINCDB may be found at:\\
        \href{https://unincdb.nekostein.com/dbindex.pdf}{https://unincdb.nekostein.com/dbindex.pdf}
    \item The Charter of the witnessed unincorporated organization is available at the following URL:\\
        \input{.workdir/UNINC.toml.Nekostein.charter-href.texpart}
    \item The unincorporated organization has requested letters of witness from the following witness agencies.
    \begin{itemize}
        \input{.workdir/UNINC.toml.Nekostein.99.texpart}
    \end{itemize}
\end{enumerate}

\hsepline




\end{document}



% Notes:
% - Run `nekostein-installvilib.sh' to install Nekostein VI lib.
